\textbf{How to measure maximally precise radial velocities from a set of spectra:\\ The time-independent spectrum case}

### 2021-06-12 paper/eprv.tex
up to 6.3.1

\documentclass[modern]{aastex63}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[sort&compress]{natbib}
\usepackage[hang,flushmargin]{footmisc}

@@

\acknowledgements
It is a pleasure to thank
  Jacob Bean (Chicago),
  John Brewer (Yale),
  Dan Foreman-Mackey (Flatiron),
  Ben Montet (Chicago),
  Hans-Walter Rix (MPIA),
  Julian Stuermer (Chicago),
and the participants in the weekly Stars Group Meeting at the Flatiron
Institute for valuable contributions to this project.
None of this would have been possible without the incredible effort
of the \HARPS\ team and \acronym{ESO}, who built the instrument and made the
data used here public.
MB thanks the Max-Planck-Institut f\"ur Astronomie in Heidelberg
for hospitality during a critical phase of this project.

@@

\todo{...add software tags}

>>>>

\documentclass[modern]{aastex631}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[sort&compress]{natbib}
\usepackage[hang,flushmargin]{footmisc}

@@

\begin{acknowledgements}
It is a pleasure to thank
  Jacob Bean (Chicago),
  John Brewer (Yale),
  Dan Foreman-Mackey (Flatiron),
  Ben Montet (Chicago),
  Hans-Walter Rix (MPIA),
  Julian Stuermer (Chicago),
and the participants in the weekly Stars Group Meeting at the Flatiron
Institute for valuable contributions to this project.
None of this would have been possible without the incredible effort
of the \HARPS\ team and \acronym{ESO}, who built the instrument and made the
data used here public.
MB thanks the Max-Planck-Institut f\"ur Astronomie in Heidelberg
for hospitality during a critical phase of this project.

@@

\todo{...add software tags}
\end{acknowledgements}
